### 2018-05-16 results.Rnw
update fig6 legend

\begin{figure}[!h]
	%  	\includegraphics[width=1\textwidth]{fig/fig-5.pdf}
	\caption{{\bf Wavelet analysis of positional data.}
		A: Raw position data for a representative female (top) and male (bottom) \emph{Drosophila~melanogaster} over five days, in black. 
		The thick coloured lines show the average position every two hours.
		The green rectangles in the background show the two time windows selected for B and C.
		B: Close up of the first time window in A, showing position over one hour, starting at the beginning of the L phase of day 1.
		C: Close up of the second time window in A, showing position over one hour, starting at the middle of the L phase of day 1.
		D: Continuous wavelet transform spectrogram for the two representative animals.
		E: Average spectrogram across 40 males and 40 females.
		In D and E, the lines on the right show the marginal power spectra corresponding to the shown spectrograms (average across all time).
		The male data was collected and described in our previous study \cite{geissmann_ethoscopes_2017} (controls in figure~5M-P) and the females data was acquired in parallel, in the same experimental conditions, but not previously published.
	}
	\label{fig:fig-6}
\end{figure}

>>>>

\begin{figure}[!h]
	%  	\includegraphics[width=1\textwidth]{fig/fig-5.pdf}
	\caption{{\bf Wavelet analysis of positional data.}
		A: Raw position data for a representative female (top) and male (bottom) \emph{Drosophila~melanogaster} over five days, in black. 
		The thick coloured lines show the average position every two hours.
		The green rectangles in the background show the two time windows selected for B and C.
		B: Close up of the first time window in A, showing position over one hour, starting at the beginning of the L phase of day 1.
		C: Close up of the second time window in A, showing position over one hour, starting at the middle of the L phase of day 1.
		D: Continuous wavelet transform spectrogram for the two representative animals.
		E: Average spectrogram across 40 males and 40 females.
		In D and E, the lines on the right show the marginal power spectra corresponding to the spectrograms shown -- that is the average across 12 hours in either the light (white bar) or dark (black bar) phase.
		The male data was collected and described in our previous study \cite{geissmann_ethoscopes_2017} (controls in figure~5M-P) and the females data was acquired in parallel, in the same experimental conditions, but not previously published.
	}
	\label{fig:fig-6}
\end{figure}
